LAGOS lake depth

### 2020-07-08 figures/01_contrasts.Rmd
finish a working bathy representativness fig

>>>>

```{r gg_effort, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 3.5}
# compare characteristics of bathy lakes versus overall lakes

# load LAGOSUS DEPTH
lg_raw <- lagosus_load("depth")$depth$depth
lg <- lg_raw %>%
  mutate(lagos_effort = 
           forcats::fct_collapse(lg_raw$lagos_effort, 
                                 bathymetry = "bathymetry", 
                                 other = c("LAGOSNE", "manual", "NLA")))

# library(tigris)
# urbanareas <- tigris::urban_areas()
# urbanareas <- st_as_sf(urbanareas)
# urbanareas <- st_transform(urbanareas, LAGOSUSgis:::albers_conic())
# urbanareas <- tidyr::separate(urbanareas, NAME10,
#                               c("urban_name", "urban_state"), sep = ", ")
# urbanareas <- dplyr::filter(urbanareas, !(urban_state %in% c("AK", "HI")))
# urbanareas <- urbanareas[st_area(urbanareas) > 
#                      units::as_units(9500000, "m2"),]
# for(i in seq_len(nrow(urbanareas))){
#   print(i)
#   urbanareas[i,] <- rmapshaper::ms_simplify(urbanareas[1,])
# }
# saveRDS(urbanareas, "../data/urbanareas.rds")
urbanareas <- readRDS("../data/urbanareas.rds")

lg$urban_distance <- apply(
  st_distance(
    st_transform(
      LAGOSUS::coordinatize(lg, crs = 4326), 
      LAGOSUSgis:::albers_conic()),
    urbanareas), 
  1, function(x) x[which.min(x)])

cowplot::plot_grid(
  gg_quantdot(lg, lagos_effort, "lake_maxdepth_m"), 
  gg_quantdot(lg, lagos_effort, "lake_waterarea_ha") +
    scale_y_log10(), 
  gg_quantdot(lg, lagos_effort, "urban_distance"),
  ncol = 1)
```
